Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-29 paper/section-general-framework.tex
Fix a minor typo

An index context $\Delta = (i_1\mathord:s_1,\ldots,i_n\mathord:s_n)$ is
interpreted as cartesian product,x i.e., $\semSort{\Delta} \isDefinedAs \semSort{s_1}
\times\cdots \times \semSort{s_n}$. 
For each well-sorted index expression $\Delta \vdash
e : s$, we assign a function $\semIndexExp{e} : \semSort{\Delta} \to
\semSort{s}$ by recursion on the structure of~$e$:
\begin{align*}
\semIndexExp{i} \rho & \isDefinedAs \rho(i) &
\semIndexExp{\indexOp{f}(e_1, \ldots, e_n)} \rho & \isDefinedAs \semIndexExp{\indexOp{f}}(
\semIndexExp{e_1}\rho,\ldots,\semIndexExp{e_n}\rho)
\end{align*}

>>>>

An index context $\Delta = (i_1\mathord:s_1,\ldots,i_n\mathord:s_n)$ is
interpreted as cartesian product, i.e., $\semSort{\Delta} \isDefinedAs \semSort{s_1}
\times\cdots \times \semSort{s_n}$. 
For each well-sorted index expression $\Delta \vdash
e : s$, we assign a function $\semIndexExp{e} : \semSort{\Delta} \to
\semSort{s}$ by recursion on the structure of~$e$:
\begin{align*}
\semIndexExp{i} \rho & \isDefinedAs \rho(i) &
\semIndexExp{\indexOp{f}(e_1, \ldots, e_n)} \rho & \isDefinedAs \semIndexExp{\indexOp{f}}(
\semIndexExp{e_1}\rho,\ldots,\semIndexExp{e_n}\rho)
\end{align*}
